Temperature Measurements in Optical Tweezer Experiments

### 2016-12-29 doc/draft1.tex
more runs

@@

The second one is the thermostatting force $\mathbf{\eta}_i$, which is defined as

@@

    \mathbf{\eta}_i = 

@@

%This is done by adding for instance two regions to the simulation, one providing an influx of heat
%and the other acting as a heat sink. The algorithm is furthermore designed to incorporate the velocities of the center of mass of the system and the
%velocities of the regions.

>>>>

    \label{eq:kineticK}

@@

The second one is the thermostatting force $\boldsymbol{\eta}_i$, which is defined as

@@

    \boldsymbol{\eta}_i = 

@@

This algorithm can be applied to the problem of the levitating nano sphere in the laser beam by adjusting the setup and some of the parameters.\\
Firstly, the setup of the heat sinks and sources has to be changed. Since there is only energy pumped into the system from the outside, the region
acting as a heat sink vanishes and the region acting as a heat source spans over the whole simulation box. This means that, using the 
notation of fig. \ref{fig:ehex}, $\Omega = \Gamma_1$. Furthermore, neither the simulation box nor the heat source are moving, i.e. 
$\mathbf{v}_\Omega = \mathbf{v}_{\Gamma_1} = 0$. This affects the non-translational kinetic energy term $\mathcal{K}_{\Gamma_1}$, the thermostatting
force $\boldsymbol{\eta}$ and the correction term $\mathcal{E}\mathbf{r}$. Since there is only one region acting as a heat sink, the terms $\Delta Q$,
$\mathcal{K}$ and $\mathcal{F}$ don't need an index. The summation index in \eqref{eq:kineticK} and \eqref{eq:bigeps} can be changed to the number of
particles in the system, $N$, since all the particles are within the heat exchanging region. The masses are set to 1, i.e. $m_i = 1$ with the chosen
reduced units and with this the total mass of the region (in the term $1/m_{\Gamma_{k(\mathbf{r}_i)}}$ in \eqref{eq:bigeps}) is equal to the number of
particles in the system. With these changes, the quantities can be written down as:
    \mathcal{K} &=& \sum_{N} \frac{v_i^2}{2}\\
    \xi &=& \sqrt{1+\frac{\Delta Q}{\mathcal{K}}}\\
    \mathcal{F} &=& \frac{\Delta Q}{\Delta t}\\
    \boldsymbol{\eta}_i &=& 
    \dfrac{\mathcal{F}}{{2\mathcal{K}}} \
        \mathbf{v}_i\\
        \mathcal{E}{r}_{i,\alpha} &=& \dfrac{\eta_{i,\alpha}}{\mathcal{K}} \left[
        \frac{\mathcal{F}}{48} + \frac{1}{6} \sum_{N} \mathbf{f}_j \cdot \mathbf{v}_j
            \right] \nonumber \\
            &-& \frac{\mathcal{F}}{12\mathcal{K}} \left[
            {f_{i,\alpha}} - \frac{1}{N} \sum_{N}f_{j,\alpha}\right]
This means that the laser is modeled to be pumping energy into the system, which increases the velocities of the velocities of the particles in the
system over time, while the center of mass motion is not affected by this.\\

\subsection{Surrounding Gas - Barostat}
Without any equilibrating mechanism the setup described by now would lead to the system melting, which is not desirable. In the next step we will 
introduce the surrounding gas of the gas chamber that will absorb some of the energy in the system, leading to the final state.\\
Generally, pressure is introduced to the system by surrounding the object of interest (in this case the glass nano sphere) with a pressure medium.
There are two main requirements for the choice of such a pressure medium: the exerted pressure must be hydrostatic and the computation of the
interaction between the pressure medium and the object of interest must not take up a lot of resources.\\
The model used in this thesis was developed by Gr\"unwald and Dellago \cite{Gruenwald2006} and uses an ideal gas of non-interacting particles as
pressure medium. The particles of this pressure medium flow into the simulation from an outside box, whose geometry is based on the form of the object
of interest. This barostat also acts as a thermostat and thus is suitable for the application in this thesis.\\
The gas particles interact with the object via a soft-sphere potential of the form
\begin{equation}
    \label{eq:softsphere}
    U(r) = \frac{1}{r^{12}}
\end{equation}
in reduced units. \\
BLABLABLA\\
The algorithm can be performed by following these steps:
\begin{enumerate}
    \item Randomly draw the number of particles that are created on a single side of the minimal volume of cells, $N_\text{fac}$, from the
        distribution 
        \begin{equation}
            \langle N_\text{fac}\rangle = \Delta t L^2 P \left(\frac{1}{2\pi m k_B T}\right)^\frac12
        \end{equation}
        where $\Delta T$ is the time step of the simulation, $L$ is the side length of the cell in which the particle is created, $P$ is the desired
        pressure, $m$ is the mass of the gas particle, $k_B$ is the Boltzmann constant (which will be set to 1 in reduced units) and $T$ is the
        desired temperature. This chosen number of particles is then equally distributed over the face of the cell on which they are created.
    \item wos
\end{enumerate}

%This is done by adding for instance two regions to the simulation, one providing an influx of heat
%and the other acting as a heat sink. The algorithm is furthermore designed to incorporate the velocities of the center of mass of the system and the
%velocities of the regions.
